### 2019-02-21 paper_00_fluiddyn_meta/article.tex
Update template and python dependencies

\documentclass{../jors}

\begin{document}

{\bf Software paper for submission to the Journal of Open Research Software} \\

To complete this template, please replace the blue text with your own. The paper
has three main sections: (1) Overview; (2) Availability; (3) Reuse potential.

Please submit the completed paper to: editor.jors@ubiquitypress.com

\section*{(1) Overview}

\vspace{0.5cm}

\section*{Title}

@@

FluidDyn: a Python open-source framework for research and teaching in fluid
dynamics by simulations, experiments and data processing

\section*{Paper Authors}

% \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% 2. Last name, first name; etc.}

1. AUGIER Pierre$^a$\\
2. MOHANAN Ashwin Vishnu$^b$\\
3. BONAMY Cyrille$^a$\\

\smallskip

$^a$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\
$^b$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.

\section*{Paper Author Roles and Affiliations}
% \textcolor{blue}{1. First author role and affiliation \\
% 2. Second author role and affiliation etc.}

1. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France\\
2. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
Sweden; \\
3. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\

\section*{Abstract}

@@

\href{http://fluiddyn.readthedocs.io}{FluidDyn} is a project to foster
open-science and open-source in the fluid dynamics community.  It is thought of as
a research project to channel open-source dynamics, methods and tools to do
science.
%
We propose a set of Python packages forming a framework to study fluid dynamics
with different methods, in particular laboratory experiments (package
\fluidpack{lab}), simulations (packages \fluidpack{fft}, \fluidpack{sim} and
\fluidpack{foam}) and data processing (package \fluidpack{image}).
%
In the present article, we give an overview of the specialized packages of the
project and then focus on the base package called \fluidpack{dyn}, which contains
common code used in the specialized packages.  Packages \fluidpack{fft} and
\fluidpack{sim} are described with greater detail in two companion papers,
\citet{fluidfft, fluidsim}.
%
With the project FluidDyn, we demonstrate that specialized scientific code can
be written with methods and good practices of the open-source community. The
Mercurial repositories are available in Bitbucket
(\url{https://bitbucket.org/fluiddyn/}). All codes are documented using Sphinx
and Read the Docs, and tested with continuous integration run on Bitbucket
Pipelines and Travis.
%
To improve the reuse potential, the codes are as modular as possible, leveraging
the simple object-oriented programming model of Python.
%
All codes are also written to be highly efficient, using C++, Cython and
Pythran to speedup the performance of critical functions.

\section*{Keywords}

% \textcolor{blue}{keyword 1; keyword 2; etc. \\
% Keywords should make it easy to identify who and what the software will be
% useful for.}

Fluid dynamics research with Python. Numerical simulations. Laboratory
experiments. Free and open-source software, modular, object-oriented,
collaborative, efficient, tested, documented.

@@

Science is mainly a collective activity.  We can go further only by
\href{https://en.wikipedia.org/wiki/%
Standing_on_the_shoulders_of_giants}{``standing on the shoulders of giants''}
(and of a huge number of technicians and scientists).  Science is a lot about
how to build new knowledge from the work of others and hence, the exchange
of ideas is a fundamental aspect.
%
In the last decades, we have lived through a revolution on how people exchange
ideas.
%
Computers of all kinds (from smartphones to HPC clusters) connected by a world
wide web are used for human communication and also for many other applications.
%
It has become nearly effortless to reproduce and exchange ideas and data.
%
The set of intangibles that grows when shared and degrades when hoarded, such as
knowledge and love, has been somehow extended.
% Relevant quote:
% O Goddess Saraswati, your Treasure is unique in nature.  It increases when it
% is freely spent and gets destroyed if it is hoarded (and not shared with
% others).
%
The information technology revolution open doors to fantastic opportunities for
human collaboration, and of course, for science.

@@

\section*{Implementation and architecture}

@@

\section*{Software location:}

% {\bf Archive} \textcolor{blue}{(e.g. institutional repository, general
% repository) (required – please see instructions on journal website for
% depositing archive copy of software in a suitable repository)}

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] PyPI
\item[Persistent identifier:] https://pypi.org/project/fluiddyn
\item[Licence:] CeCILL-B, a BSD compatible French licence.
\item[Publisher:] Pierre Augier
\item[Version published:] 0.2.4
\item[Date published:] 02/07/2018
\end{description}

{\bf Code repository}
% \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] Bitbucket
\item[Persistent identifier:] https://bitbucket.org/fluiddyn/fluiddyn
\item[Licence:] CeCILL-B
\item[Date published:] 2015
\end{description}

% {\bf Emulation environment} \textcolor{blue}{(if appropriate)}

@@

\section*{Language}

% \textcolor{blue}{Language of repository, software and supporting files.}

English

@@

\bibliographystyle{../agsm}
\bibliography{../bib}

@@

\end{document}

>>>>

% % \documentclass{../jors}

% \begin{document}

% {\bf Software paper for submission to the Journal of Open Research Software} \\

% To complete this template, please replace the blue text with your own. The paper
% has three main sections: (1) Overview; (2) Availability; (3) Reuse potential.

% Please submit the completed paper to: editor.jors@ubiquitypress.com

% \rule{\textwidth}{1pt}

% \section*{(1) Overview}

% \vspace{0.5cm}

% \section*{Title}

@@

% FluidDyn: a Python open-source framework for research and teaching in fluid
% dynamics by simulations, experiments and data processing

% \section*{Paper Authors}

% \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% 2. Last name, first name; etc.}
%
% 1. AUGIER Pierre$^a$\\
% 2. MOHANAN Ashwin Vishnu$^b$\\
% 3. BONAMY Cyrille$^a$\\
%
% \smallskip
%
% $^a$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
% Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\
% $^b$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.
%
% \section*{Paper Author Roles and Affiliations}
% \textcolor{blue}{1. First author role and affiliation \\
% 2. Second author role and affiliation etc.}

% 1. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France\\
% 2. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
% Sweden; \\
% 3. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\

% \section*{Abstract}

@@

% \href{http://fluiddyn.readthedocs.io}{FluidDyn} is a project to foster
% open-science and open-source in the fluid dynamics community.  It is thought of as
% a research project to channel open-source dynamics, methods and tools to do
% science.
% %
% We propose a set of Python packages forming a framework to study fluid dynamics
% with different methods, in particular laboratory experiments (package
% \fluidpack{lab}), simulations (packages \fluidpack{fft}, \fluidpack{sim} and
% \fluidpack{foam}) and data processing (package \fluidpack{image}).
% %
% In the present article, we give an overview of the specialized packages of the
% project and then focus on the base package called \fluidpack{dyn}, which contains
% common code used in the specialized packages.  Packages \fluidpack{fft} and
% \fluidpack{sim} are described with greater detail in two companion papers,
% \citet{fluidfft, fluidsim}.
% %
% With the project FluidDyn, we demonstrate that specialized scientific code can
% be written with methods and good practices of the open-source community. The
% Mercurial repositories are available in Bitbucket
% (\url{https://bitbucket.org/fluiddyn/}). All codes are documented using Sphinx
% and Read the Docs, and tested with continuous integration run on Bitbucket
% Pipelines and Travis.
% %
% To improve the reuse potential, the codes are as modular as possible, leveraging
% the simple object-oriented programming model of Python.
% %
% All codes are also written to be highly efficient, using C++, Cython and
% Pythran to speedup the performance of critical functions.

% \section*{Keywords}

% % \textcolor{blue}{keyword 1; keyword 2; etc. \\
% % Keywords should make it easy to identify who and what the software will be
% % useful for.}

% Fluid dynamics research with Python. Numerical simulations. Laboratory
% experiments. Free and open-source software, modular, object-oriented,
% collaborative, efficient, tested, documented.

@@

Science is mainly a collective activity.  We can go further only by
\href{https://en.wikipedia.org/wiki/Standing\_on\_the\_shoulders\_of\_giants}{``standing
on the shoulders of giants''}
(and of a huge number of technicians and scientists).  Science is a lot about
how to build new knowledge from the work of others and hence, the exchange
of ideas is a fundamental aspect.
%
In the last decades, we have lived through a revolution on how people exchange
ideas.
%
Computers of all kinds (from smartphones to HPC clusters) connected by a world
wide web are used for human communication and also for many other applications.
%
It has become nearly effortless to reproduce and exchange ideas and data.
%
The set of intangibles that grows when shared and degrades when hoarded, such as
knowledge and love, has been somehow extended.
% Relevant quote:
% O Goddess Saraswati, your Treasure is unique in nature.  It increases when it
% is freely spent and gets destroyed if it is hoarded (and not shared with
% others).
%
The information technology revolution open doors to fantastic opportunities for
human collaboration, and of course, for science.

@@

\section{Implementation and architecture}

@@

% \section*{Software location:}
%
% % {\bf Archive} \textcolor{blue}{(e.g. institutional repository, general
% % repository) (required – please see instructions on journal website for
% % depositing archive copy of software in a suitable repository)}
%
% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] PyPI
% \item[Persistent identifier:] https://pypi.org/project/fluiddyn
% \item[Licence:] CeCILL-B, a BSD compatible French licence.
% \item[Publisher:] Pierre Augier
% \item[Version published:] 0.2.4
% \item[Date published:] 02/07/2018
% \end{description}
%
% {\bf Code repository}
% % \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}
%
% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] Bitbucket
% \item[Persistent identifier:] https://bitbucket.org/fluiddyn/fluiddyn
% \item[Licence:] CeCILL-B
% \item[Date published:] 2015
% \end{description}
%
% {\bf Emulation environment} \textcolor{blue}{(if appropriate)}

@@

% \section*{Language}
%
% % \textcolor{blue}{Language of repository, software and supporting files.}
%
% English

@@

@@
